---
title: "iteration and list columns"
output: github_document
---

```{r}
library(tidyverse)
library(knitr)
library(rvest)

knitr::opts_chunk$set(
  fig.width = 6, 
  fig.asp = .6, 
  out.width = "90%"
)
```

iteration = doing the same thing over and over 
- doing the same thing with the same function over and over --> iterating 

for loops 
- loops are the easiest place to start
- loops have an output object, a sequence to iterate over, the loop body, and (optionally) an input object 
- basic structure: 

input = list(_)
output = list(_)

for (i in 1:n) {
    output[[i]] = f(input[[i]])
    
}

Loop functions
- loop process (supply input vector/ list; apply a function to each element; save the result to a vector/ list) is really common 
- for loops can get tedious/ opaque 
- loop functions are popular for cleaning up loops 
    - we focus on purr::map()
    - base R has lapply() and similar things - DONT USE THESE

map
- goal of map is to clarify the loop process 
- basic structure: (input is the list I need to iterate over)
  ouput = map(input, f)
- benefit is clarity 

map variants 
- map takes one input and returns a list (by default) 
- you can use specific variants to prevent errors (know the form that you will output)
  map_dbl, map_lgl, map_ df
- if you need to iterate over 2 inputs - you can use map variants to give 2 inputs 

Process for iteration: 
- write a single example, embed example into a loop, abstract loop body to a function, re-write using a map statement
- make sure something works and then try to iterate however feels most natural 

LISTS: 
- dataframes provide a nice data rectangle (UNIFORM) = special list 
- ouputs that are less uniform/ nicely structured = LIST 
- you can put anything in the list (including a list) 
- list columns --> df 

## Lists 

```{r}
l = list(
  vec_numeric = 5:8, 
  vec_logical = c(TRUE, FALSE), 
  summary = summary(rnorm(1000, mean = 5, sd = 3))
)

l[[3]]

l[["summary"]]

l$summary
```

Looks nothing like a dataframe 

## list of normals

```{r}
list_norms = 
  list(
    a = rnorm(50, mean = 2, sd = 1), 
    b = rnorm(50, mean = 5, sd = 3), 
    c = rnorm(50, mean = 20, sd = 1.2), 
    d = rnorm(50, mean = -12, sd = 0.5) 
  )
```

what if we want to take the mean and sd of this list? 

```{r}
mean_and_sd = function(x) {
  
  if(!is.numeric(x)) {
    stop("x needs to be numeric")
  }
  if(length(x) < 3) {
    stop("x should have at least 3 numbers")
  }
  mean_x = mean(x) 
  sd_x = sd(x)
  
  output_df = 
    tibble(
      mean = mean_x, 
      sd = sd_x
    )
  
  return(output_df)
  
}

mean_and_sd(list_norms[[1]])
mean_and_sd(list_norms[[2]])
mean_and_sd(list_norms[[3]])
mean_and_sd(list_norms[[4]])
```

Why use numbers instead of letters (use element #x instead of remembering the names each time)

## for loop 

Let's use a for loop to iterate over my list of normals. 

```{r}
output = vector("list", length = 4)

for(i in 1:4) {
  
  output[[i]] = mean_and_sd(list_norms[[i]])
  
}


```

let's use map instead ...

```{r}
output = map(list_norms, mean_and_sd) 

output = map(list_norms, median) 

output = map(list_norms, summary) 

output = map(list_norms, IQR) 
```

default outputs as a list 

```{r}
output = map_dbl(list_norms, median)
```

## LIST COLUMNS!! 

```{r}
list_col_df = 
  tibble(
    name = c("a", "b", "c", "d"), 
    norms = list_norms
  )
```

it has lists in one of the columns but we can do normal things to dataframes 

```{r}
list_col_df %>% 
  filter(name == "a")

list_col_df %>% 
  pull(name) 

list_col_df %>% 
  pull(norms) 

list_col_df$norms[[1]]

mean_and_sd(list_col_df$norms[[1]])
mean_and_sd(list_col_df$norms[[2]])
mean_and_sd(list_col_df$norms[[3]])
mean_and_sd(list_col_df$norms[[4]])

list_col_df %>% 
  mutate(summaries = map(norms, mean_and_sd)) 

list_col_df %>% 
  mutate(summaries = map(norms, mean_and_sd)) %>% 
  pull(summaries)
```

playing with various ways of extracting list elements from a list column

## Nested data

When would you atually end up with a dataframe inside of a dataframe? 

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

We have a lot of information nested into one study item (Central Park, Waterhole, Waikiki)

Nest data within location  

```{r}
weather_nested = nest(weather_df, data = date:tmin)

weather_nested %>% 
  filter(name == "CentralPark_NY") %>% 
  pull(data) 

weather_nested %>% 
  pull(data) 
```

Let's do something with linear regression - let's say we want to see how tmax is related to tmin

```{r}
weather_nested$data[[1]]
weather_nested$data[[2]]
weather_nested$data[[3]]

lm(tmax ~tmin, data = weather_nested$data[[1]])
lm(tmax ~tmin, data = weather_nested$data[[2]])
lm(tmax ~tmin, data = weather_nested$data[[3]])

weather_lm = function(df) {
  
  lm(tmax ~tmin, data = df)

}

weather_lm(weather_nested$data[[1]])

lm(tmax ~tmin, data = weather_nested$data[[1]])

```

bottom two things are the same (using function vs. not) 

I want to have another column inside of my dataset that is the result of the linear model fit 

```{r}
map(weather_nested$data, weather_lm) 

weather_nested %>% 
  mutate(lm_results = map(data, weather_lm))

```

You can also unnest

```{r}
unnest(weather_nested, data)

weather_nested %>% 
  unnest(data)
```

Can also use pipes 

## Revist Napoleon 

Function to get reviews/ stars

```{r}
get_page_reviews = function(page_url) {
  
  page_html = read_html(page_url)

  review_titles = 
    page_html %>%
    html_elements(".a-text-bold span") %>%
    html_text()
  
  review_stars = 
    page_html %>%
    html_elements("#cm_cr-review_list .review-rating") %>%
    html_text()
  
  review_text = 
    page_html %>%
    html_elements(".review-text-content span") %>%
    html_text()
  
  reviews = 
    tibble(
      title = review_titles,
      stars = review_stars,
      text = review_text
  )
  
  return(reviews)
  
}


base_url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="

urls = str_c(base_url, 1:5)

map(urls, get_page_reviews)

napoleon_df = 
  tibble(
    urls = urls
)

napoleon_df %>% 
  mutate(reviews = map(urls, get_page_reviews)) %>% 
  select(reviews) %>% 
  unnest()

```



