---
title: "iteration"
output: github_document
---

```{r}
library(tidyverse)
library(knitr)
library(rvest)

knitr::opts_chunk$set(
  fig.width = 6, 
  fig.asp = .6, 
  out.width = "90%"
)
```

When to write funtions - if you have to use the code more than twice 

Parts to a function: 

- arguments (inputs) 
  these get used by the cody in the body (i.e., x in mean(x)) - na.rm = FALSE is the default, but you'll sometimes was to change things 
  
- body (code that does stuff) 
  starts with data/ input checks using conditional execution (check that whatever input you provide is allowed in the function that you created) , performs operations, format output 
  
- return objects (what the function produces) 
  implicit - last value produced by the function or explicit - return a specific thing 
  can return single values or a collection of values (he prefers returning dataframes)
  named or unnamed 
  
SCOPING 
- will help prevent/ identify errors
- if you have x in your function, it'll look in the function and then if its not there then itll look in your environment. 
- this will be a problem if you have x in the function and also x in the workspace, it can cross over if there are issues 

CONDITIONAL EXECUTION 
- going through some checks at the beginning of the body of the function 
Code: if (condition_1) {thing_1} 
else if (condition_2) {thing_2}
else {thing_3}

HOW TO WRITE FUNCTIONS 
- start with the smallest possible, least complicated version 
- if it works, then add complexity 

## Start coding 

## Z scores

subtract mean and divide by the standard deviation 

```{r}
x_vec = rnorm(25, mean = 5, sd = 4) 

(x_vec - mean(x_vec)) / sd(x_vec)
```

Decide we want to do this to a lot of different vectors 

```{r}
z_scores = function(x) {
  
  z = (x - mean(x)) / sd(x)
  
  return(z)
  
}
```

Function of an x input, 
body of function within curly brackets 

I want to use argument x 
THEN return z

Now try to use it

```{r}
z_scores(x = x_vec)
```

Looks like the same collection of z scores 

```{r}
y_vec = rnorm(40, mean = 12, sd = .3) 

z_scores(y_vec)

```

How great is this! 

```{r, error = TRUE}
z_scores(3)

z_scores(c("my", "name", "is", "christie"))

mtcars

z_scores(mtcars)

```

NA is probably not what i want to have happen

ERROR 

ERROR

The things that are going wrong here, my function shouuld work if I give it a collection of numbers that I can take the mean of 

Update z_scores function to be better

```{r, error = TRUE}
z_scores = function(x) {
  
  if(!is.numeric(x)) {
    stop("x needs to be numeric")
  }
  if(length(x) < 3) {
    stop("x should have at least 3 numbers")
  }
  z = (x - mean(x)) / sd(x)
  
  return(z)
  
}
```

If something is going to break, it should break early and informatively 

## Multiple outputs 

If I give you something things, I want the mean and standard deviation 

```{r}
mean_and_sd = function(x) {
  
  if(!is.numeric(x)) {
    stop("x needs to be numeric")
  }
  if(length(x) < 3) {
    stop("x should have at least 3 numbers")
  }
  mean_x = mean(x) 
  sd_x = sd(x)
  
  output_df = 
    tibble(
      mean = mean_x, 
      sd = sd_x
    )
  
  return(output_df)
  
}
```

```{r}
mean_and_sd(y_vec)
mean_and_sd(x_vec)
```

Defined x as y_vec then you can work things through without doing the full function just using the environment, but you have to be careful of this 

Every once in a while, you should restart your session or do rm(x) from the environment to make sure things still work 

## Different sample sizes, means, and sds

```{r}
sim_data = 
  tibble(
  x = rnorm(30, mean = 2, sd = 3) 
  )

sim_data %>% 
  summarize(
    mean = mean(x), 
    sd = sd(x)
  )
```

Let's write a function that simulates data, computes the mean and sd. 

mu and sigma are the true things 

allows multiple function inputs which map to different things in my code 

everything should be self contained

```{r}
sim_mean_sd = function (n, mu, sigma) {
  
  # do checks on inputs 
  
  sim_data = 
    tibble(
    x = rnorm(n, mean = mu, sd = sigma) 
    )
  
  sim_data %>% 
    summarize(
      mean = mean(x), 
      sd = sd(x)
    )
  
}

sim_mean_sd(30, 4, 3)

```

## Revisit Napolean Dynamite 

```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_elements(".a-text-bold span") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_elements("#cm_cr-review_list .review-rating") %>%
  html_text()

review_text = 
  dynamite_html %>%
  html_elements(".review-text-content span") %>%
  html_text()

reviews = 
  tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
)

```

Okay but there are a lot of pages of reviews 

Could copy and paste everything above to page number 2, 3, 4, 5, and update the reviews df to 2, 3, 4, etc. 

Instead, write a function that gets reviews based on page url

```{r}
get_page_reviews = function(page_url) {
  
  page_html = read_html(page_url)

  review_titles = 
    page_html %>%
    html_elements(".a-text-bold span") %>%
    html_text()
  
  review_stars = 
    page_html %>%
    html_elements("#cm_cr-review_list .review-rating") %>%
    html_text()
  
  review_text = 
    page_html %>%
    html_elements(".review-text-content span") %>%
    html_text()
  
  reviews = 
    tibble(
      title = review_titles,
      stars = review_stars,
      text = review_text
  )
  
  return(reviews)
  
}

page_url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

get_page_reviews(page_url)

url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=2"

get_page_reviews(url)

url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=3"

get_page_reviews(url)

base_url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="

urls = str_c(base_url, 1:5)

bind_rows(
  get_page_reviews(urls[1]),
  get_page_reviews(urls[2]),
  get_page_reviews(urls[3]),
  get_page_reviews(urls[4]),
  get_page_reviews(urls[5]))
```

Supposed I want to change something else - you can also add that into the function (i.e., get rid of the \n at the beginning of the function)

You can pass in a summary function into your function (i.e., summarize this vector using the mean, median, standard deviation, etc.) - useful in factor reorder according to the median 

EXAMPLE OF SCOPING

```{r}
f = function(x) {
  z = x + y 
  z
}

x = 1
y = 2 

f(x = y) 
```





